The Birth of a Galaxy: Population III Progenitors and Metal-enriched Stellar Populations

### 2010-10-04 ms.tex
Added preliminary versions of figures 1 and 2.  Debating whether to discuss a third (gas-poor) halo.

\title{The Birth of a Galaxy: Self-consistent transition to Population
  II Star Formation}

@@

Here we present the gaseous and stellar evolution of two selected
halos in the simulation, starting with the birth of the first Pop III
star in its merger history.  We then compare the nature of star
formation in these two halos.

@@

@@

>>>>

\title{The Birth of a Galaxy: Population III Progenitors and
  Metal-enriched Stellar Populations}

@@

Here we present the gaseous and stellar evolution of three selected
halos in the simulation: (1) a halo that never recovers a gas
reservior after a PISN, (2) one that experiences a series of major
mergers, and (3) one that has an early mass buildup but no major
mergers after $z=12$.  The halos are referred to by these numbers.  We
start with the birth of the first Pop III star in its merger history.
We then compare the nature of star formation in these halos.

\li Should we present the gas-poor halo?

@@

\begin{figure}
  \epsscale{1.15}
  \plotone{f1}
  \caption{\label{fig:evo}}
  \epsscale{1}
\end{figure}

\begin{figure*}
  \plotone{f2}
  \caption{\label{fig:projections}}
\end{figure*}

@@

\li Need to run the halo analysis on smaller halos to capture the
entire merger histories.
